Load the libraries
```{r}
library(zoo)
library(xts)
library(quantmod)
library(tidyverse)
library(PerformanceAnalytics)
library(tidyquant)
library(timetk)
library(PortfolioAnalytics)
library(ROI)
library(ROI.plugin.glpk)
library(ROI.plugin.quadprog)

help("periodReturn")
```
Get the tickers 
Note the fund inception of VEA was July 27, 2007 so I started with August 1, 2007
I did not start at July 27 so monthly returns and deviations were not biased 
by the truncated amount of monthly data. Perhaps this does not matter. 

Calculated monthly returns as this tends to be the standard for portfolio 
optimizatoin calculations. Whether or not its the best or daily returns should
be computed is something to look into. 
```{r}
stocks_simple_portfolio <- c("spy", "rsp", "ijh", "ijr", "vnq", "tip", 
                             "vwehx", "lqd", "vwo", "vea", "gld") %>% 
  tq_get(get = "stock.prices",
         from = "2007-08-01",
         to = "2021-12-31") %>% 
  group_by(symbol) %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "daily",
               col_rename = "ret",
               type = 'log')

stocks_simple_portfolio
```
To run performance analytics the data must be in type xts
```{r}
returns_xts <- stocks_simple_portfolio %>% 
  select(symbol, date, ret) %>% 
  spread(symbol, value = ret) %>% 
  tk_xts()
head(returns_xts)
```
Calculate Mean Return and Covariance Matrix
```{r}
mean_ret <- colMeans(returns_xts)
cov_mat <- cov(returns_xts) * 252
print(round(cov_mat,4))
```
Set up a random simulation of portfolio weights.  Make sure weights sum to zero
```{r}
weights <- runif(n = 11, 0, 1)
weights <- weights/sum(weights)
weights

```
Calculate Portfolio returns, risk, sharpe ratio set-up 
```{r}
#port_returns <- (sum(weights * mean_ret) + 1)^252 - 1
#stddev <- sqrt(t(weights)) %*% (cov_mat %*% weights)
#Sharpe Ratio
#rfr = 0
#sratio <- (port_returns - rfr) / stddev
```
Compute Efficient Frontier using a for loop to simulate 5000 portfolios
```{r}
theoretical_ports <- 1000000
all_weights <- matrix(nrow = 1000000,
                     ncol = 11)
#empty vector to store portfolio returns
port_returns <- vector('numeric', length=1000000)
#same for risk
port_stddev <- vector('numeric', length=1000000)
port_sratios <- vector('numeric', length=1000000)
#the loop 
for(i in seq_along(port_returns)) {
  weights <- runif(n = 11, 0, 1)
  weights <- weights/sum(weights)
  #store theoretical weight in vector
  all_weights[i,] <- weights
  #
  port_ret <- sum(weights * mean_ret) 
  port_ret <- ((port_ret + 1)^252) - 1
  port_returns[i] <- port_ret
  #
  stddev <- sqrt(t(weights)) %*% (cov_mat %*% weights)
  port_stddev[i] <- stddev
  #
  #rfr = 0
  sratio <- port_ret / stddev
  port_sratios[i] <- sratio
}
```
Store the heavy lifting in a table
```{r}
theo_port_tib <- tibble(Return = port_returns,
                        Risk = port_stddev,
                        SharpeRatio = port_sratios)
colnames(all_weights) <- colnames(returns_xts)

theo_port_tib <- tk_tbl(cbind(all_weights, theo_port_tib))

theo_port_tib %>% 
  arrange(desc(SharpeRatio))
```
Find minimum variance portfolio and max sharpe ratio portfolio
```{r}
min_var <- theo_port_tib[which.min(theo_port_tib$Risk),]
max_sharpe <- theo_port_tib[which.max(theo_port_tib$SharpeRatio),]
high_return <- theo_port_tib[which.max(theo_port_tib$Return),]

```
Plot Efficient Frontier
```{r}
theo_port_tib %>% 
  ggplot(aes(x = Risk, y = Return, color = SharpeRatio)) +
  geom_point() +
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(labels = scales::percent) +
  labs(x = 'Annualized Risk',
       y = 'Annualized Returns',
       title = "Efficient Frontier") +
  geom_point(aes(x = Risk,
                 y = Return), data = min_var, color = 'green') +
  geom_point(aes(x = Risk,
                 y = Return), data = max_sharpe, color = 'purple') +
  geom_point(aes(x = Risk,
                 y = Return), data = high_return, color = 'red') 
  #annotate('text', x = 0.10, y = 0.1, label = "Tangency Portfolio") +
  #annotate('text', x = 0.1, y = 0.1, label = "Minimum variance portfolio") 
  
``` 
Plot Weights Max Sharpe
```{r}
max_sharpe %>% 
  gather(gld:vwo, key = Asset,
         value = Weights) %>%
  mutate(Asset = as.factor(Asset)) %>%
  ggplot(aes(x = fct_reorder(Asset,Weights), y = Weights, fill = Asset)) +
  geom_bar(stat = 'identity') +
  theme_minimal() +
  labs(x = 'Assets', y = 'Weights', title = "Tangency Portfolio Weights") +
  scale_y_continuous(labels = scales::percent)
```
Plot Min Variance
```{r}
min_var %>% 
gather(gld:vwo, key = Asset,
         value = Weights) %>%
  mutate(Asset = as.factor(Asset)) %>%
  ggplot(aes(x = fct_reorder(Asset,Weights), y = Weights, fill = Asset)) +
  geom_bar(stat = 'identity') +
  labs(x = 'Assets', y = 'Weights', title = "Minimum Variance Portfolio Weights") +
  scale_y_continuous(labels = scales::percent) 
```
Plot Max Return
```{r}
high_return %>% 
gather(gld:vwo, key = Asset,
         value = Weights) %>%
  mutate(Asset = as.factor(Asset)) %>%
  ggplot(aes(x = fct_reorder(Asset,Weights), y = Weights, fill = Asset)) +
  geom_bar(stat = 'identity') +
  theme_minimal() +
  labs(x = 'Assets', y = 'Weights', title = "Maximum Returns") +
  scale_y_continuous(labels = scales::percent) 
```
Create a table showing number of shares to purchase
```{r}
Last_Close_Price <- c("spy", "rsp", "ijh", "ijr", "vnq", "tip", 
                             "vwehx", "lqd", "vwo", "vea", "gld") %>% 
  tq_get(get = "stock.prices",
         from = "2021-12-31",
         to = "2021-12-31") %>% 
  group_by(symbol)
```

Initialize Portfolio Spec Object for user defined portfolio
Add constraint for 100% investment, prohibit short sales, and the 
target return rate
```{r}
stock_max_return <- max(colMeans(returns_simple_pfolio))
max_return <- stock_max_return 
  
asset_names <- colnames(returns_simple_pfolio)
pspec <- portfolio.spec(assets = asset_names)
pspec <- add.constraint(portfolio = pspec, type = "full_investment")
pspec <- add.constraint(portfolio = pspec, type = "long_only")
pspec <- add.objective(portfolio=pspec, type="risk", name = "StdDev")
pspec <- add.objective(portfolio=pspec, type="return", name = "mean")

opt <- optimize.portfolio(returns_simple_pfolio, portfolio = pspec, optimize_method= "ROI", Sha)

portfolio_weights <- c(extractWeights(opt))

asset_name_tibble <- c(sort(c("spy", "rsp", "ijh", "ijr", "vnq", "tip", "vwehx", "lqd", "vwo",
             "vea", "gld")))

names(portfolio_weights) <- asset_name_tibble

tib_optml_weights <- tibble(asset_name_tibble, portfolio_weights)


tib_optml_weights

```
Bar Chart of Portfolio Weights
```{r}
tib_optml_weights %>% 
  group_by(asset_name_tibble) %>% 
  ggplot(aes(x = asset_name_tibble, y=portfolio_weights, fill = asset_name_tibble)) +
    geom_col() +
    labs(x = "Investment") +
    labs(y = "Weight")
    
  
```



Min_Variance_Portfolio
```{r}
colnames <- c('a', 'b', 'c')
values <- c(1,2,3)
names(values) <- colnames

tib <- tibble()
tib <- bind_rows(tib, values)


```


